\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-20 jss/article.tex
small correction2
any chanage

But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other. In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side. We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line). For reference, we could have plotted this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans     8.75 12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy to read summary of the results of the estimation. In the Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$ and as such those schools whose variation within the school is less than between the variation schools will shrink greater than $50\%$. The results provide by \code{gpb} suggests that there is little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0. \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[scale=0.3]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

@@

                    obs.mean   se prior.mean shrinkage low.intv post.mean
Unit w/ min(se)        -1.00  9.0      8.168     0.408  -13.297     2.737
Unit w/ median(se)1     1.00 11.0      8.168     0.507  -13.027     4.633
Unit w/ median(se)2     7.00 11.0      8.168     0.507   -8.780     7.592
Unit w/ max(se)        12.00 18.0      8.168     0.734  -10.208     9.189
Overall Mean            8.75 12.5      8.168     0.552   -9.163     8.168

                     upp.intv post.sd
                       16.692   7.634
                       20.131   8.441
                       23.602   8.257
                       29.939  10.227
                       25.723   8.900

Second-level Variance Component Estimation Summary:
alpha = log(A) for Gaussian and log(1/r) for Binomial and Poisson data:

  post.mode.alpha post.sd.alpha
1           4.768         1.139

@@

         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429  0.0462
2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420  0.0448
3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411  0.0437
4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403  0.0429
5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396  0.0424
6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341  0.0415
7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331  0.0400
8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323  0.0388
9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315  0.0380
10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379  0.0432
11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302  0.0377
17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297  0.0381
18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410\end{CodeOutput}
\end{CodeChunk}
Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715). The estimation results including $\hat{r}=113$ follows.

>>>>

But the point estimates are not enough to evaluate hospital reliabilities because one hospital may have a lower point estimate but  bigger uncertainty (variance) than the other. In the second plot of Figure \ref{fig:hospshr}, the estimated 95\% intervals are displayed on the right-hand side. We see that each posterior mean (red dot) is between the sample mean (empty dot) and the second-level mean (a blue horizontal line). For reference, we could plot this 95\% interval plot by the order of data input via \code{plot(p, sort = FALSE)}.

@@

         obs.mean   se prior.mean shrinkage low.intv post.mean upp.intv post.sd
5           -1.00  9.0      8.168     0.408  -13.297     2.737   16.692   7.634
2            8.00 10.0      8.168     0.459   -7.255     8.077   23.361   7.810
7           18.00 10.0      8.168     0.459   -1.289    13.484   30.821   8.176
4            7.00 11.0      8.168     0.507   -8.780     7.592   23.602   8.257
6            1.00 11.0      8.168     0.507  -13.027     4.633   20.131   8.441
1           28.00 15.0      8.168     0.657   -2.315    14.979   38.763  10.560
3           -3.00 16.0      8.168     0.685  -17.130     4.650   22.477  10.096
8           12.00 18.0      8.168     0.734  -10.208     9.189   29.939  10.227
colMeans          12.5      8.168     0.552   -9.163     8.168   25.723   8.900
\end{CodeOutput}
\end{CodeChunk}
The output from \code{gbp} provides an easy to read summary of the results of the estimation. In the Normal-Normal hierarchical model the amount of shrinkage for each unit is governed by the shrinkage factor, $B_i = V_i/(V_i + A)$ and as such those schools whose variation within the school is less than between the variation schools will shrink greater than $50\%$. The results provide by \code{gpb} suggests that there is little evidence that the training provided much of an added benefit with every school's $95\%$ posterior interval containing 0. \pkg{Rgbp} also provides functionality to plot the results of the analysis as seen in Figure \ref{fig:8schoolsplot}.

@@

\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3in]{school1.png}
\caption{Shrinkage plot and 95\% interval plot for 8 schools}
\label{fig:8schoolsplot}
\end{center}
\end{figure}

@@

                      obs.mean   se prior.mean shrinkage low.intv post.mean
Unit with min(se)        -1.00  9.0       8.17     0.408   -13.30      2.74     
Unit with median(se)1     1.00 11.0       8.17     0.507   -13.03      4.63     
Unit with median(se)2     7.00 11.0       8.17     0.507    -8.78      7.59     
Unit with max(se)        12.00 18.0       8.17     0.734   -10.21      9.19     
Overall Mean                   12.5       8.17     0.552    -9.16      8.17

                      upp.intv post.sd
                          16.7    7.63
                          20.1    8.44
                          23.6    8.26
                          29.9   10.23
                          25.7    8.90

  post.mode.alpha post.sd.alpha post.mode.A
1            4.77          1.14         118

@@

         obs.mean  n   X1 prior.mean shrinkage low.intv post.mean upp.intv post.sd
1           0.400 45 1.00      0.310     0.715    0.248     0.335    0.429  0.0462
2           0.378 45 1.00      0.310     0.715    0.244     0.329    0.420  0.0448
3           0.356 45 1.00      0.310     0.715    0.240     0.323    0.411  0.0437
4           0.333 45 1.00      0.310     0.715    0.236     0.316    0.403  0.0429
5           0.311 45 1.00      0.310     0.715    0.230     0.310    0.396  0.0424
6           0.311 45 0.00      0.233     0.715    0.179     0.256    0.341  0.0415
7           0.289 45 0.00      0.233     0.715    0.175     0.249    0.331  0.0400
8           0.267 45 0.00      0.233     0.715    0.171     0.243    0.323  0.0388
9           0.244 45 0.00      0.233     0.715    0.166     0.237    0.315  0.0380
10          0.244 45 1.00      0.310     0.715    0.210     0.291    0.379  0.0432
11          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
12          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
13          0.222 45 0.00      0.233     0.715    0.161     0.230    0.308  0.0377
14          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
15          0.222 45 1.00      0.310     0.715    0.202     0.285    0.375  0.0441
16          0.200 45 0.00      0.233     0.715    0.155     0.224    0.302  0.0377
17          0.178 45 0.00      0.233     0.715    0.148     0.218    0.297  0.0381
18          0.156 45 0.00      0.233     0.715    0.140     0.211    0.292  0.0389
colMeans          45 0.44      0.267     0.715    0.191     0.267    0.351  0.0410
\end{CodeOutput}
\end{CodeChunk}
Our model reflects on the additional information, \emph{i.e.}, indicator covariate (1 for outfielder and 0 for other positions), estimating two different prior means, 0.310 and 0.233. Also note that the shrinkage estimates are the same for all players due to the fact that they are determined solely by the relative amount of information between the first-level and the second-level hierarchies, ($\hat{B}_{j}\equiv \hat{r} / (\hat{r}+45)$ = $113 / (113+45)$ = 0.715). The estimation results including $\hat{r}=113$ follows.
